Modern BTree\\ techniques

### 2020-01-11 btree/presentation.tex
Suffix truncation and references

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=north west lines, pattern color=red, draw=red}}
\tikzset{btree-key-prefix/.style={btree-key, minimum height=0.2cm, fill=red, opacity=0.5}}
\tikzset{btree-key-compare/.style={btree-key, minimum height=0.6cm, fill=blue, opacity=0.5}}
\tikzset{arrow-pointer/.style={
        single arrow,
        minimum height=1.5cm,
        inner sep=3pt,
        line width=1pt,
        draw,
        color=gray,
        single arrow tip angle=45,
        single arrow head extend=0.1cm
    }
}
\tikzset{btree-indirection/.style={btree-key, minimum width=0.2cm, inner sep=0, pattern=none}}
\tikzset{btree-page-header/.style={btree-key, minimum width=0.5cm, inner sep=0, pattern=none}}

@@

@@

    \end{overprint}
    \end{center}
\end{frame}
\note{
    Not a normalized version, but whole column version is in PG12
}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.center) -- ([yshift=\shift]key1\i.center);
            }
        \end{tikzpicture}
        \end{center}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.center) -- ([yshift=\shift]key1\i.center);
            }
        \end{tikzpicture}
        \end{center}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.center) -- ([yshift=\shift]key1\i.center);
            }

          \linespread{0.5}
          \node[draw, below=1cm of indirection-key12.east, minimum width=1cm, minimum height=1cm, text width=1cm, align=center, rounded corners]
              (cpu-cache) {\footnotesize{CPU\\Cache}};

@@

>>>>

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-empty/.style={btree-pointer, dashed}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}
\tikzset{btree-high-key/.style={btree-key, pattern=north west lines, pattern color=red, draw=red}}
\tikzset{btree-key-prefix/.style={btree-key, minimum height=0.2cm, fill=red, opacity=0.5}}
\tikzset{btree-key-compare/.style={btree-key, minimum height=0.6cm, fill=blue, opacity=0.5}}
\tikzset{arrow-pointer/.style={
        single arrow,
        minimum height=1.5cm,
        inner sep=3pt,
        line width=1pt,
        draw,
        color=gray,
        single arrow tip angle=45,
        single arrow head extend=0.1cm
    }
}
\tikzset{btree-indirection/.style={btree-key, minimum width=0.2cm, inner sep=0, pattern=none}}
\tikzset{btree-page-header/.style={btree-key, minimum width=0.5cm, inner sep=0, pattern=none}}
\tikzset{cpu-cache/.style={draw, minimum width=1cm, minimum height=1cm, text width=1cm, align=center, rounded corners}}
\tikzset{cpu-cache-hide/.style={cpu-cache, draw=none, color=white}}

@@

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        R. C. Singleton, "An efficient algorithm for sorting with minimal
        storage", Communications of the ACM, vol. 12, no.3 pp. 185-186, 1969
    \linespread{1.5}

@@

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        R. Bayer, K. Unterauer, "Prefix B-trees", ACM Transactions on Database
        Systems, vol. 2, no. 1, pp. 11-26, 1977
    \linespread{1.5}

    \end{center}
\end{frame}
\note{
    Not a normalized version, but whole column version is in PG12
}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.east) -- ([yshift=\shift]key1\i.center);
            }
          \linespread{0.5}
          \node[cpu-cache-hide, below=1cm of indirection-key12.east]
              (cpu-cache) {\footnotesize{CPU\\Cache}};

          \coordinate[above=2cm of cpu-cache.north east] (cpu-cache-top-left);
          \coordinate[above=2cm of cpu-cache.north west] (cpu-cache-top-right);
          \draw[draw=none] ([xshift=-0.2cm]cpu-cache.north east) -- ([xshift=-0.2cm]cpu-cache-top-left);
          \draw[draw=none] ([xshift=0.2cm]cpu-cache.north west) -- ([xshift=0.2cm]cpu-cache-top-right);

        \end{tikzpicture}
        \end{center}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.east) -- ([yshift=\shift]key1\i.center);
            }

          \linespread{0.5}
          \node[cpu-cache-hide, below=1cm of indirection-key12.east]
              (cpu-cache) {\footnotesize{CPU\\Cache}};

          \coordinate[above=2cm of cpu-cache.north east] (cpu-cache-top-left);
          \coordinate[above=2cm of cpu-cache.north west] (cpu-cache-top-right);
          \draw[draw=none] ([xshift=-0.2cm]cpu-cache.north east) -- ([xshift=-0.2cm]cpu-cache-top-left);
          \draw[draw=none] ([xshift=0.2cm]cpu-cache.north west) -- ([xshift=0.2cm]cpu-cache-top-right);

        \end{tikzpicture}
        \end{center}

@@

            \foreach \i/ \shift in {1/0.35cm,2/0.11cm,3/-0.07cm,4/-0.3cm} {
                \draw[->, btree-line] ([yshift=\shift]indirection-key1\i.east) -- ([yshift=\shift]key1\i.center);
            }

          \linespread{0.5}
          \node[cpu-cache, below=1cm of indirection-key12.east]
              (cpu-cache) {\footnotesize{CPU\\Cache}};

@@

    \linespread{0.5}
    \vspace{0.5cm}
    \color{black}\fontsize{6pt}{0}\selectfont
        G. Graefe, Per-Ake Larson, "B-tree indexes and CPU caches",
        International Conference on Data Engineering, pp. 349-358, 2001
    \linespread{1.5}
